Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-14 publication_materials/ms_rbc.tex

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.

Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS. Should that be the case, it is crucial that we discover and classify such states.

In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. 
Marginal stability is required at each successive timestep to constrain the perturbation amplitudes. 
A similar strategy is employed by \cite{michel_chini_2019}, where an analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially. 
We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.

\section{Model Setup}\label{sec:model}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
The equations of motion are then given by
\begin{align}
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
\end{align}
where $p$ is pressure and $T$ is temperature. 
For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, boundary temperature difference, kinematic viscosity, and thermal diffusivity respectively. For convenience, we define
\begin{equation}
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
\end{equation}

To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
\begin{align}
    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z, t) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z, t) + A(t) p'(x, z, t) \label{EQ:reynolds_dc_p}.
\end{align}
where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. Perturbations must admit no horizontal-average; an arbitrary perturbation $f'$ obeys
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
\begin{equation}
  \langle T'^2 \rangle_{\mathcal{D}} = 1
\end{equation}
thereby alleviating any ambiguity in $A(t)$. 
Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
\begin{equation}
  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$. It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$. However we must have $\bar{w}(z, t) = 0$ due to incompressibility.

@@

At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).

\section{Perturbation Evolution}
Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A(t)$. 
To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
Stable modes decay away rapidly. 
Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop. Only marginally stable modes can traverse this hypothetical time-scale separation. Therefore the amplitude function $A(t)$ must satisfy
\begin{equation}
    \max_{k_x} \{ \omega \} = 0.
\end{equation}

For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE) $\bar{T}_{\rm{MSTE}}$, thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.

@@

\subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes. If ignored, we are forced to reduce the timestep and allow the modes to alternate. Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
\begin{equation}
    A^2 \langle w' b' \rangle_x = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{x, \, n}
\end{equation}
where  $\langle w' b' \rangle_{x, \, n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
In general, we expect a function $\mathbf{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). 
We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known. 
Difficulty arises when transitioning between different numbers of marginal modes. 
Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive. 
Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated. 
In general we find that no other obvious course of action yields equilibria.

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are solutions to the quasilinear form of the Rayleigh-B\'enard convection equations derived in section \ref{sec:model}. 
For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
Their mean temperatures $\bar{T}_{\rm{MSTE}}$ are symmetric about $z = 0$ by construction.

@@

    \caption{Mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 

@@

Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ states. 
In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their respective adjacencies. 
Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x and the smaller mode is denoted with a +. 
In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$. 
The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
For $Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the blue branch and the green branch. 
This development is associated with relatively thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch (green) and those of the bulk-domain-oriented smallest branch (blue).

@@

The Nusselt number, which describes convective performance, is given by
\begin{equation}
  \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
\end{equation}
There is no general consensus surrounding the scaling behavior $\Nu \sim Ra^{\beta}$ for high $Ra$ systems. The asymptotic value of $\beta$ is of particular importance in astrophysical systems. In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, DNS, along with several ECS. 
The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
More specifically, $\beta = 1/3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} and \cite{Cvitanovic} inhibiting heat flux. 
Alternatively, we might anticipate the existence of exact coherent states with smaller $\Nu$, forming another node in the Markov chain whose long-term behavior agrees with the simulation data.

\section{Simulations with Thermally Equilibrated Initial Conditions}
This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. 
Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with the linear initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= 0.5 - z \\
    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
    p(x, z)\big|_{t=0} &= 0.
\end{align}
$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
We define the MSTE initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= \bar{T}_{\rm{MSTE}}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
\end{align}
Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
The $\sqrt{2}$ factor is necessary for eigenfunction normalization.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=3.4in]{sim_eq_nu.png}
%     \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
%     \label{fig:nu_sim}
% \end{figure}
The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}. 
This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale
\begin{equation}
    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
\end{equation}
Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably. Further, this suggests that the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$
% \begin{figure}
%     \centering
%     \includegraphics[width=3.4in]{sim_eq_ke.png}
%     \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$). The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state. Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
%     \label{fig:ke_sim}
% \end{figure}
\begin{figure}
    \begin{minipage}{3.4in}
        \centering
        \includegraphics[width=3.4in]{sim_eq_nu.png}
        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization. For high $Ra$ simulations, researchers often choose to recycle the results of similar $Ra$ runs \cite{Verzicco, Johnston} because the high-Reynolds number flows associated with the convective transient period are computationally prohibitive \cite{Anders_AE}.}
        \label{fig:nu_sim}
    \end{minipage}
\end{figure}

@@

\section{Discussion}\label{sec:Discussion}
In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus_1954}. 
They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
We also obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
Thus solutions might be unique, but we cannot demonstrate this rigorously.

>>>>

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.

Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen,chini_cells}. 
Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS. Should that be the case, it is crucial that we discover and classify such states.

In \cite{michel_chini_2019}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially. 
We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.

\section{Model Setup}\label{sec:model}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
The equations of motion are then given by
\begin{align}
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
\end{align}
where $p$ is pressure and $T$ is temperature. 
For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, boundary temperature difference, kinematic viscosity, and thermal diffusivity respectively. For convenience, we define
\begin{equation}
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
\end{equation}

To derive the quasilinear form, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
\begin{align}
    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z, t) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z, t) + A(t) p'(x, z, t) \label{EQ:reynolds_dc_p}.
\end{align}
where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. Perturbations must admit no horizontal-average; an arbitrary perturbation $f'$ obeys
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
Assuming the existance of nontrivial solutions, we also fix the volume-average 
\begin{equation}
  \langle \langle T'^2 \rangle_x \rangle_z = 1
\end{equation}
thereby alleviating any ambiguity in $A(t)$. 
Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
\begin{equation}
  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$. It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$. However we must have $\bar{w}(z, t) = 0$ due to incompressibility.

@@

At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).

\section{Perturbation Evolution}
Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A(t)$. 
To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
Stable modes decay away rapidly. 
Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop. Only marginally stable modes can traverse this hypothetical time-scale separation. Therefore the amplitude function $A(t)$ must satisfy
\begin{equation}
    \max_{k_x} \{ \omega \} = 0.
\end{equation}

For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle$.

@@

\subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes. If ignored, we are forced to reduce the timestep and allow the modes to alternate. Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
\begin{equation}
    A^2 \langle w' b' \rangle = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{n}
\end{equation}
where  $\langle w' b' \rangle_{n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
In general, we expect a function $\mathbf{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). 
We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known. 
Difficulty arises when transitioning between different numbers of marginal modes. 
Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive. 
Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated. 
In general we find that no other obvious course of action yields equilibria.

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are solutions to the quasilinear form of the Rayleigh-B\'enard convection equations derived in section \ref{sec:model}. 
For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
Solutions are symmetric about $z = 0$ by construction.

@@

    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 

@@

Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ states. 
In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their respective adjacencies. 
Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x and the smaller mode is denoted with a +. 
In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$. 
The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
For $Ra \geq 10^8$, a third branch appears (shown in red), splitting the widening gap between the blue branch and the green branch. 
This development is associated with relatively thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch (green) and those of the bulk-domain-oriented smallest branch (blue).

@@

Nusselt numbers $\Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}. 
The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} and \cite{Cvitanovic} inhibiting heat flux. 
Alternatively, we might anticipate the existence of exact coherent states with smaller $\Nu$, forming another node in the Markov chain whose long-term behavior agrees with the simulation data.

\section{Simulations with Thermally Equilibrated Initial Conditions}
This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. 
Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with the linear initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= 0.5 - z \\
    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
    p(x, z)\big|_{t=0} &= 0.
\end{align}
$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
We define the MSTE initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
\end{align}
Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
The $\sqrt{2}$ factor is necessary for eigenfunction normalization.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=3.4in]{sim_eq_nu.png}
%     \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
%     \label{fig:nu_sim}
% \end{figure}
The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}. 
This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale
\begin{equation}
    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
\end{equation}
Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably. Further, this suggests that the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle \langle |\mathbf{u}|^2 \rangle_x \rangle_z$
% \begin{figure}
%     \centering
%     \includegraphics[width=3.4in]{sim_eq_ke.png}
%     \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$). The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state. Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
%     \label{fig:ke_sim}
% \end{figure}
\begin{figure}
    \begin{minipage}{3.4in}
        \centering
        \includegraphics[width=3.4in]{sim_eq_nu.png}
        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization. For high $Ra$ simulations, researchers often choose to recycle the results of similar $Ra$ runs \cite{Verzicco, Johnston} because the high-Reynolds number flows associated with the convective transient period are computationally prohibitive \cite{Anders_AE}.}
        \label{fig:nu_sim}
    \end{minipage}
\end{figure}

@@

\section{Discussion}\label{sec:Discussion}
In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus_1954}. 
They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$. 
Thus solutions might be unique, but we cannot demonstrate this rigorously.
